Numerical modeling of artificial heart valve

### 2015-05-17 citech-2015/Paper-template/paper.tex
LanguageToolCheck fixes

\section{Introduction}
The importance of medical researches of human blood circulatory system can hardly be overestimated,
because this kind of knowledge is extremely practical and significant. Annualy approximately 250 000
surgeries are performed in the world to restore or replace damaged heart valves \cite{yoganathan}, and the
quantity is expected to increase \cite{yacoub}. The solution of scientific and technical problems of the artificial valves 
creation depends on correct understanding of the interaction between blood flow and valve leaflets. Mathematical modeling
of artificial heart valves performance enables to get thorough understanding of its internal processes in order to improve its design.
There are many researches devoted to the mathematical and numerical modeling
of heart valve performance, based on which two main problem solution approaches were defined.

@@

Fig. \ref{fig:valve_in_mixture} shows, that initial uniform admixture distribution is interrupted by the valve leaflets motion. Eventually oscillatory mode of
admixture motion can be recognized that corresponds to valve operating cycle. 
Moreover the Fig. \ref{fig:valve_in_mixture} shows that admixture distribution over a cross section being parallel to axis $Oy$
is not symmetric because the valve leaflets are not symmetric about the axis $Oy$ as well.

@@

\bibitem{pilhwa_2010} Pilhwa L., Boyce E.G., Peskin C.S.: The immersed boundary method for advection-electrodiffusion with implicit timestepping and local mesh refinement. Comput Phys. 229(13), (2010)

>>>>

\section{Introduction}
The importance of medical researches of human blood circulatory system can hardly be overestimated,
because this kind of knowledge is extremely practical and significant. Annually approximately 250 000
surgeries are performed in the world to restore or replace damaged heart valves \cite{yoganathan}, and the
quantity is expected to increase \cite{yacoub}. The solution of scientific and technical problems of the artificial valves 
creation depends on correct understanding of the interaction between blood flow and valve leaflets. Mathematical modeling
of artificial heart valves performance enables to get thorough understanding of its internal processes in order to improve its design.
There are many researches devoted to the mathematical and numerical modeling
of heart valve performance, based on which two main problem solution approaches were defined.

@@

Fig. \ref{fig:valve_in_mixture} shows, that initial uniform admixture distribution is interrupted by the valve leaflets motion. Eventually oscillatory mode of
admixture motion can be recognized that corresponds to valve operating cycle. 
Moreover, the Fig. \ref{fig:valve_in_mixture} shows that admixture distribution over a cross section being parallel to axis $Oy$
is not symmetric because the valve leaflets are not symmetric about the axis $Oy$ as well.

@@

\bibitem{pilhwa_2010} Pilhwa L., Boyce E.G., Peskin C.S.: The immersed boundary method for advection-electrodiffusion with implicit time stepping and local mesh refinement. Comput Phys. 229(13), (2010)
